R Notebook

### 2016-07-15 finalwriteup/trial_code_eq.rmd
finished editing method

>>>>

| Date    | Hours | Charge Amount (\$)| Cost Amount (\$)| Created By | Discipline | Job No. | Reconciled | Scope       |
|---------|-------|---------------|-------------|------------|------------|---------|------------|-------------|
| 2014/09/01 | 4     | 640           | 400         | P12        | Civil      | 1.2.300 | Yes        | Concept     |
| 2014/09/03 | 4.5   | 720           | 450         | P12        | Civil      | 1.2.300 | Yes        | Preliminary |
| 2014/09/03 | 2     | 480           | 320         | P34        | Civil      | 1.2.300 | Yes        | Preliminary |
| 2014/09/08 | 7     | 1120          | 700         | P12        | Civil      | 1.2.300 | Yes        | Preliminary |
| 2014/09/09 | 1     | 160           | 100         | P12        | Civil      | 1.2.300 | Yes        | Preliminary |
| 2014/09/15 | 3     | 390           | 240         | P3         | Structural | 1.2.400 | Yes        | Site        |
| ...     | ...   | ...           | ...         | ...        | ...        |         | ...        | ...         |\
\\
